Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-20 finalReportPres.tex
Updated Final Presentation

\begin{frame}{Modeling Vehicle Subsystems}{System Requirements}
	\begin{block}{Specifications}
	\begin{minipage}[t]{0.62\linewidth}    
    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
    		\item Resulting plant model will consist of reasonably accurate subsystem models
    		\item Subsystems can be used to create a HIL testbench
    		\item Steering model can handle very small changes in steering angles
		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
	\begin{minipage}[t]{0.34\linewidth}
	\begin{figure}[h]
    		\captionsetup{justification=centering, margin=0.5cm}
    		\includegraphics[width=1.5in]{figs/inkscape/nonlinearBehavior}
    		\caption{Steering Non-linear Behavior}
    		\label{fig:nonlinGraph}

@@

  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%

@@

%  \todo[inline]{Where are the detailed simulink block diagram for each subsystem?}
	\begin{figure}
		\centering \includegraphics[width=.35\linewidth]{figs/img/steeringNeuralNetworkDetailedSystem}\quad%
		\caption{Steering Neural Network Simulink Model Subsystem}
		\centering \begin{minipage}[b][0.35\textheight][c]{.35\linewidth} 
%		\begin{itemize} \item HIL Bench 						
%		\item Measuring output voltages to confirm results \end{itemize} 
		\end{minipage}\\[1em]
		\centering \includegraphics[width=.35\linewidth]{figs/img/accelNeuralNetworkDetailedSystem}\quad%
		\caption{Acceleration Neural Network Simulink Model Subsystem}
		\centering \includegraphics[,width=.35\linewidth]{figs/img/brakeNeuralNetworkDetailedSystem}
		\caption{Brake Neural Network Simulink Model Subsystem}
	\end{figure}
\end{frame}

\begin{frame}{Validation and Testing}{Validation Setup}
	\begin{figure}
		\centering \includegraphics[width=.35\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}\quad%
		\centering \begin{minipage}[b][0.35\textheight][c]{.35\linewidth} \begin{itemize} \item HIL Bench 						\item Measuring output voltages to confirm results \end{itemize} \end{minipage}\\[1em]
		\centering \includegraphics[angle=270,width=.35\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}\quad%
		\centering \includegraphics[angle=270,width=.35\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
	\end{figure}
\end{frame}

\begin{frame}{Validation and Testing}{Model Validation}
	\begin{figure}
		\centering \includegraphics[width=.45\linewidth]{figs/img/aStuffValidationBrakeModel}\quad%
		\caption{Model Validation Setup}
    			\label{fig:validationSetup}
		\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{itemize} \item Testing data points using Control Desk software  \end{itemize} \end{minipage}\\[1em]
	\end{figure}
\end{frame}

%\begin{frame}{Transfer Function Modeling}{Steering System}
%	\begin{block}{}
% \begin{itemize}
%	\item Best fit percentage of the by-wire steering estimated model is 83.25
%	\item Best fit percentage of the manual steering estimated model is 90.27
% \end{itemize}
% \begin{figure}
%    \centering
%    \begin{minipage}{0.45\textwidth}
%        \centering
%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
%        \caption{Output of Estimated By-Wire System Model}
%        \label{fig:byWireSteerModel}
%    \end{minipage}\hfill
%    \begin{minipage}{0.45\textwidth}
%        \centering
%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
%        \caption{Output of Estimated Manual System Model}
%        \label{fig:manualSteerModel}
%    \end{minipage}
%\end{figure}
%  \end{block}
%\end{frame}

%\begin{frame}{Transfer Function Modeling}{Acceleration System}
%	\begin{block}{}
% \begin{itemize}
%	\item Best fit percentage of the by-wire acceleration estimated model is 97.75
%	\item Best fit percentage of the manual acceleration estimated model is 98.3
% \end{itemize}
% \begin{figure}
%    \centering
%    \begin{minipage}{0.45\textwidth}
%        \centering
%        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
%        \caption{Output of Estimated By-Wire System Model}
%        \label{fig:byWireAccelModel}
%    \end{minipage}\hfill
%    \begin{minipage}{0.45\textwidth}
%        \centering
%        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
%        \caption{Output of Estimated Manual System Model}
%        \label{fig:manualAccelModel}
%    \end{minipage}
%\end{figure}
%  \end{block}
%\end{frame}

%\begin{frame}{Transfer Function Modeling}{Brake System}
%\begin{block}{}
% \begin{itemize}
%	\item Only manual models were considered 
%	\item There were no transfer function models that could satisfy both the best fit and error requirements 
% \end{itemize}
%% \begin{figure}
%%    \centering
%%    \begin{minipage}{0.45\textwidth}
%%        \centering
%%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
%%        \caption{Output of Estimated By-Wire System Model}
%%        \label{fig:byWireSteerModel}
%%    \end{minipage}\hfill
%%    \begin{minipage}{0.45\textwidth}
%%        \centering
%%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
%%        \caption{Output of Estimated Manual System Model}
%%        \label{fig:manualSteerModel}
%%    \end{minipage}
%%\end{figure}
%  \end{block}
%\end{frame}

%\begin{frame}{Neural Network Modeling}{Steering System}
%	\begin{block}{}
%  		\begin{figure}[H]
%  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
%			\item Only a few samples are just outside of the accuracy requirements
%			\item Transfer function model did not meet the accuracy requirements
%			\end{itemize} \end{minipage}\\[1em]
%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
%  		\end{figure}
%	\end{block}
%\end{frame}

%\begin{frame}{Neural Network Modeling}{Acceleration System}
%	\begin{block}{}
%  		\begin{figure}[H]
%  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
%			\item All samples within 2\% of the actual output
%			\item Transfer function model did not have the same accuracy bounds
%			\item Fewer concerns about connections in Simulink
%			\end{itemize} \end{minipage}\\[1em]
%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
%  		\end{figure}
%	\end{block}
%\end{frame}

%\begin{frame}{Neural Network Modeling}{Brake System}
%	\begin{block}{}
%\begin{figure}[H]
%  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
%			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
%			\item With this model, the error is kept below 5\%
%			\item Able to easily track model performance
%			\item Provides better results than the transfer function model
%			\end{itemize} \end{minipage}\\[1em]
%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
%			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
%  		\end{figure}
%	
%  \end{block}
%\end{frame}

@@

\begin{frame}{References}
  \bibliographystyle{IEEEtran}
  \bibliography{bib/references.bib}
\end{frame}

>>>>

\begin{frame}{Modeling Vehicle Subsystems}{System Requirements}
	\begin{block}{Specifications}
	\begin{minipage}[t]{0.62\linewidth}    
    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
	\begin{itemize}
    		\item Resulting plant model will consist of reasonably accurate subsystem models
    		\item Subsystems can be used to create a HIL testbench
    		\item Steering model can handle very small changes in steering angles
    \begin{itemize}
		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
    \end{itemize}
	\end{itemize}
	\end{minipage}
	\begin{minipage}[t]{0.34\linewidth}
	\begin{figure}[h]
		\centering
    		\captionsetup{justification=centering, margin=0.5cm}
    		\includegraphics[width=1.5in]{figs/inkscape/nonlinearBehavior}
    		\caption{Steering Non-linear Behavior}
    		\label{fig:nonlinGraph}
	\end{figure}
	\end{minipage}
\end{block}
\end{frame}
%-------------------------

\section{Simulation Results}

@@

  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeNeuralNetworkDetailedSystem}\quad%

@@

\begin{frame}{Validation and Testing}{Validation Setup}
	\begin{figure}
		\centering	
		\begin{minipage}{.5\textwidth}
	  		\centering
	  		\includegraphics[width=.85\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}
	  		%\captionof{figure}{A figure}
	  		\label{fig:test1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
	  		\centering
	  		\begin{itemize} 
	  			\item HIL Bench
	  			\item Measuring output voltages to confirm results 
	  		\end{itemize}
		\end{minipage}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\centering	
		\begin{minipage}{.5\textwidth}
	  		\centering
	  		\includegraphics[angle=270,width=.85\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}
	  		%\captionof{figure}{A figure}
	  		\label{fig:test1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
	  		\centering
	  		\includegraphics[angle=270,width=.85\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
	  		%\captionof{figure}{Another figure}
	  		\label{fig:test2}
		\end{minipage}
	\end{figure}
\end{frame}

\begin{frame}{Validation and Testing}{Model Validation}
	\begin{block}{}	
		\begin{itemize}
			\item Testing data points using Control Desk software  
		\end{itemize}		
		\begin{figure}
			\centering \includegraphics[width=.9\linewidth]{figs/img/aStuffValidationBrakeModel}
			\caption{Model Validation Setup}
    				\label{fig:validationSetup}
		\end{figure}
	\end{block}
\end{frame}

@@

\begin{frame}[allowframebreaks]{References}
  \bibliographystyle{IEEEtran}
  \bibliography{bib/references.bib}
\end{frame}
